HMM

### 2016-01-18 paper3.Rnw
BB's turn

@@

\todo{describe the Viterbi algorithm here, and the autocorrelation function
computation - everything that appears in the results should be described
explicitly here}

@@

>>>>

Model complexity and number of parameters increase as the number of latent states increase, FMM to HMM, and lastly, FMM and HMM incorportating temportal heterogeneity.

\begin{table}[]
\centering
\caption{Number of Parameters for each model type}
\label{Cat-ID}
\begin{tabular}{cccc}
 Type & Model  & Number of States & Number of Parameters  \\
  FMM & FMM & 3 & 9    \\
  FMM & FMM & 4 & 12    \\
  FMM & FMM & 5 & 15   \\
  FMM & FMM & 6 & 18  \\
  FMM + TH & FMM + TH (Sin)  & 3 & 15    \\
  FMM + TH & FMM + TH (Sin)  & 4 & 20    \\
  FMM + TH & FMM + TH (Sin)  & 5 & 25    \\
  FMM + TH & FMM + TH (Sin)  & 6 & 30    \\
  HMM & HMM & 3 & 18    \\
  HMM & HMM & 4 & 28    \\
  HMM & HMM & 5 & 40   \\
  HMM & HMM & 6 & 54  \\
  HMM + TH & HMM + TH (Block)  & 3 & 36    \\
  HMM + TH & HMM + TH (Block)  & 4 & 60    \\
  HMM + TH & HMM + TH (Block)  & 5 & 90    \\
  HMM + TH & HMM + TH (Block)  & 6 & 126    \\
  HMM + TH & HMM + TH (Quad)  & 3 & 36    \\
  HMM + TH & HMM + TH (Quad)  & 4 & 60    \\
  HMM + TH & HMM + TH (Quad)  & 5 & 90    \\
  HMM + TH & HMM + TH (Quad)  & 6 & 126    \\
  HMM + TH & HMM + TH (Sin)  & 3 & 36    \\
  HMM + TH & HMM + TH (Sin)  & 4 & 60    \\
  HMM + TH & HMM + TH (Sin)  & 5 & 90    \\
  HMM + TH & HMM + TH (Sin)  & 6 & 126    \\
  HMM + TH & HMM + TH (Hourly)  & 3 & 225    \\
  HMM + TH & HMM + TH (Hourly)  & 4 & 396

\end{tabular}
\end{table}

@@

\todo{describe the Viterbi algorithm here, and the autocorrelation function
computation - everything that appears in the results should be described
explicitly here....ML: at the bottom}

@@

<<viterbi, warning=FALSE, message=FALSE, echo=FALSE >>=
load("cat1.RData")
vitcat <- function(catt,mod){
  params <- tail(getpars(mod),6)
  vitdist <- numeric(ntimes(mod))
  states <- viterbi(mod)$state
  for(i in 1:ntimes(mod)){
    if(states[i] == 1){
      vitdist[i] <- rnorm(1,params[1],params[2])
    }
    if(states[i] == 2){
      vitdist[i] <- rnorm(1,params[3],params[4])
    }
    if(states[i] == 3){
      vitdist[i] <- rnorm(1,params[5],params[6])
    }
  }
  dat <- data.frame(viterbi=vitdist,time=catt$Time, obs=catt$LogDist)
  return(dat)
}

temp <- vitcat(cat,fithomo3s) %>% dplyr:::select(-time)%>%ldply(.,acffun)
ggplot(temp,aes(lag,ACF,colour=.id))+
geom_point()+geom_line() +theme_bw() +
ggtitle("ACF plot of BIC Selected Models")
